On the characteristic and diameter of planar integral point sets \footnote{ The work of the first author was partially supported by the Theoretical Physics and Mathematics Advancement Foundation “BASIS”. }

### 2025-02-21 char-4k-bound/char-4k-bound.tex
[4k3] Implement the Referee's comments

	In Section 2, we give all the required notions and known results. In Section 3, we discuss some examples of integral point sets in order to demonstrate that none of the classes $4k+1$, $4k+2$, $4k+3$ is too exotic nor pathological. Section 4 is devoted to the connection between Erdös curves and characteristic. In Section 5, we prove some auxiliary results, and we proceed to the main one in Section 6.

@@

In this Section, we provide rigorous definitions and list some known results.

>>>>

	In Section 2, we give all the required notions and known results. In Section 3, we discuss some examples of integral point sets in order to demonstrate that none of the classes $4k+1$, $4k+2$, $4k+3$ is too exotic nor pathological. Section 4 is devoted to the connection between Erdős curves and the characteristic. In Section 5, we prove some auxiliary results, and we proceed to the main one in Section 6.

@@

In this section, we provide rigorous definitions and list some known results.
